Mamba-Based Tumor Segmentation\\ \thanks{$\dagger$ Equal contributions}

### 2024-04-19 paper/main.tex
updated results table
update table

\centering
\begin{tabular}{|c|c|c|c|c|}
\hline
Model & Param Count & Size (MB) & Avg. IOU & Avg. Dice \\
\hline
Pyramidal Mamba & Y & Z & A & B \\
\hline
U-Mamba & Y & Z & A & B \\
\hline
U-Net & Y & Z & A & B \\
\hline
SegViT & Y & Z & A & B \\
\hline
\end{tabular}

\section{Loss Curves}
We also display the loss curves for each model. Each model was trained for 100 epochs under [OTHER CONDITIONS].

\section*{Acknowledgment}

The preferred spelling of the word ``acknowledgment'' in America is without 
an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
acknowledgments in the unnumbered footnote on the first page.

>>>>

\begin{table}[!h]
    \renewcommand{\arraystretch}{1.2}
    \setlength{\tabcolsep}{2pt}
    \centering
    \footnotesize
    \begin{tabular}{|l|c|c|c|c|}
    \hline
    Model & Params & Size & IOU & Dice \\
    \hline
    Pyramidal Mamba (Ours) & 10M & 109.15 & 0.8004 & 0.8867 \\
    \hline
    U-Mamba & 9.8M & 108.10 & 0.7908 & 0.8799 \\
    \hline
    U-Net & 7.8M & 31.09 & 0.8071 & 0.8929 \\
    \hline
    SegViT & Y & Z & A & B \\
    \hline
    ResNet18 & 13.9M & 55.76 & 0.7623 & 0.8648 \\
    \hline
    ResNet50 & 42.9M & 171.85 & 0.7661 & 0.8672 \\
    \hline
    Ultra LightM-UNet & 0.049M & 0.20 & 0.6725 & 0.7955 \\
    \hline
    \end{tabular}
    \end{table}

\section{Acknowledgment}

This work was done as a final project for the University of South Carolina's CSCE763 Digital Image Processing course taught in Spring 2024 under Dr. Yan Tong.
